Reliable feature point matching

### 2013-08-13 text/main/ch3_matching_methods.tex
A few touches on the thesis

In this chapter we will describe the algorithms used in the experiements
in detail. We start by introducing the proposed algorithms \emph{MM} and 
\emph{MMC}, and continue with the reference algorithms used for 
comparison, \emph{Ratio}, \emph{Spectral} and \emph{Isomatch}.

\section{Proposed Matching Methods}
\label{S:MatchingMethods}

@@

\begin{figure}[h]
	\centering%
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/MMC_pitts_source}
			\caption{Source image pair}
			\label{fig:pitts_source}
		\end{subfigure}%
		~ %
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/MMC_pitts_keypoints}
			\caption{Feature points}
			\label{fig:pitts_keypoints}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		%\qquad (or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/mirror_match_off}
			\caption{\emph{Ratio}}
			\label{fig:unique}
		\end{subfigure}%
		~ %add desired spacing between images, e. g. ~, \quad, 
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/mirror_match_with_pruned}
			\caption{\emph{MM} intermediate result}
			\label{fig:within}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		%\qquad (or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/mirror_match}
			\caption{\emph{MM} final result}
			\label{fig:without}
		\end{subfigure}%
		~ %add desired spacing between images, e. g. ~, \quad, 
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/MMC_partition}
			\caption{\emph{MMC} Partition Example}
			\label{fig:pitts_partition}
		\end{subfigure}%
	\caption{Feature matching with \emph{MM} and \emph{MMC}. Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.  
	(c) Result of \emph{Ratio} matching. 
  (d) All matches found by \emph{MM}, including intra-image matches. 
	(e) Final \emph{MM} result. 
	(f) Example of a partition of feature points after clustering, which 
includes similar feature points from building windows and shirt patterns.}%
	\label{fig:comparemirror}%
\end{figure}%

@@

\begin{algorithm}[htb]
\caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
\label{alg-getmatches}
%\fontsize{10}{10}\selectfont
    \begin{algorithmic}
    \Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
    all features
    \State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i)
        \neq getImg(f_j) \wedge f_i, f_j \in p \right\}$
    \If{$\left\vert edges \right\vert > 1$}
        \State $matches \gets MMGet(p, t)$
    \ElsIf{$\left\vert edges \right\vert = 1$}
        \State $matches \gets RatioGet(p, features, t)$
    \Else
        \State $matches \gets \varnothing$
    \EndIf

@@

The matching algorithm for \emph{MMC} detailed in 
Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
more than two elements using the \emph{MM} approach (\emph{MMGet}).  
However, as can be seen in the example in Figure~\ref{fig:graph-view}, 
many of the partitions contain only two feature points from different 
images linked by one edge. In this case, we compare the similarity of 
the these two feature points with their second best match and remove 
matches where this ratio lies above a certain threshold, like in the 
\emph{Ratio} algorithm (\emph{RatioGet}).  For example in the case of 
Figure~\ref{fig:pitts_partition}, we have feature points from a building 
in one image grouped together with points from a shirt pattern in 
another.  The nearest neighbor method would have returned wrong matches, 
but since we match the partition with \emph{MM}, points in the building 
end up matching other points in the building, and no matches are 
returned.

@@

\begin{algorithm}[htb]
\caption{Ratio Match (\emph{Ratio})}
\label{alg-ratio}
%{\fontsize{10}{10}\selectfont
\begin{algorithmic}
\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
\State $matches\gets \varnothing$
\State $features_1 \gets getFeatures(im_1)$
\State $features_2 \gets getFeatures(im_2)$
\ForAll{$f_i \in features_1$}
    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
    \State $ratio \gets d(f_i, f_m) / d(f_i, f_n)$
	\If{$ratio < t$}
        \State $matches \gets \left(f_i, f_m\right)$
	\EndIf
\EndFor
\Return $matches$
\end{algorithmic}
%}
\end{algorithm}

@@

@@

The \emph{Spectral} algorithm (Algorithm~\ref{alg-spectral}) used in the 
comparison of matching algorithms is based on the spectral matching 
algorithm proposed by Leordeanu and Herbert 
\cite{leordeanu2005spectral}.  The central idea behind it is that the 
set of actual correspondences of feature points between two images 
should be pairwise consistent. That is, given two feature points that 
are geometrically close in one image, for most cases we would assume 
that the closest correspondences of these two points in another image 
would be similarly close.  Based on this assumption we want to pick out 
a set of matches $T \subset S$ where $S$ is the initial set of possible 
matches such that the matches in $T$ are as pairwise consistent as 
possible. If we let $x$ be a binary vector corresponding in length to 
the set of initial matches $S$, where $x_i = 1$ if $m_i \subset T$, then 
we can formulate a subset-score as:
\begin{equation*}
	S = \sum_{m_i, m_j \in T} M(m_i, m_j) = x^TMx
\end{equation*}
The solution $x^{*}$ that maximizes this equation is then $x^{*} = 
argmax(x^TMx)$. By relaxing the constraints on $x$ such that it can take
values in the range of $\left[0, 1\right]$ we can interpret $x_i$ as the
association of $m_i$ with the optimal subset of matches $T$. Because we 
only worry about the relative values of $x$ we can fix the norm of $x$ 
to $1$, in which case by Raleigh's ratio theorem, the $x^{*}$ that 
optimizes $x^TMx$ is the principal eigenvector of $M$.

@@

Since the testing is done on images with partial overlap, the final set 
of matches returned in Algorithm~\ref{alg-spectral} is the set of 
matches where the association of the match with the optimal subset of 
matches $T$ as measured by $x^{*}$ is above a certain threshold. For 
experiments the set of initial matches were given by the best match per 
feature point and the threshold was adjusted to allow for the best 50\% 
to be included in the set of final matches. A rate less than 50\% 
usually did not improve results, so to threshold the \emph{Spectral}
algorithm we filter the output using the ratio between first and second
best match as done in \emph{Ratio}.

>>>>

In this chapter we will describe the algorithms used in the experiements
in detail. We start by introducing the proposed algorithms \emph{Mirror 
Match (MM)} and \emph{Mirror Match with Clustering (MMC)}, and continue 
with the reference algorithms used for comparison, \emph{Ratio}, 
\emph{Spectral} and \emph{Isomatch}.

\section{Proposed Matching Methods}
\label{S:MatchingMethods}
In this section we describe the two proposed algorithms for matching 
feature points \emph{Mirror Match
(MM)} and \emph{Mirror Match with Clustering (MMC)}.

@@

\begin{figure}[h]
	\centering%
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/MMC_pitts_source}
			\caption{Source image pair}
			\label{fig:pitts_source}
		\end{subfigure}%
		~ %
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/MMC_pitts_keypoints}
			\caption{Feature points}
			\label{fig:pitts_keypoints}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		%\qquad (or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/mirror_match_off}
			\caption{\emph{Ratio}}
			\label{fig:unique}
		\end{subfigure}%
		~ %add desired spacing between images, e. g. ~, \quad, 
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/mirror_match_with_pruned}
			\caption{\emph{MM} intermediate result}
			\label{fig:within}
		\end{subfigure}%
		\\ %add desired spacing between images, e. g. ~, \quad, 
		%\qquad (or a blank line to force the subfigure onto a new line)
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/mirror_match}
			\caption{\emph{MM} final result}
			\label{fig:without}
		\end{subfigure}%
		~ %add desired spacing between images, e. g. ~, \quad, 
		\begin{subfigure}[t]{0.5\columnwidth}
			\centering
			\includegraphics[width=0.95\columnwidth]{images/MMC_partition}
			\caption{\emph{MMC} Partition Example}
			\label{fig:pitts_partition}
		\end{subfigure}%
	\caption{Feature matching with \emph{MM} and \emph{MMC}. Dots represent feature points; green/red lines indicate correct/incorrect matches, respectively; black lines represent edges in the feature graph.  
	(c) Result of \emph{Ratio} matching. 
  (d) All matches found by \emph{MM}, including intra-image matches. 
	(e) Final \emph{MM} result. 
    (f) Example of a partition of feature points after clustering, which 
includes similar feature points from different sides of a building.}%
	\label{fig:comparemirror}%
\end{figure}%

@@

\begin{algorithm}[t]
\caption{Impl.\ of getMatches (\emph{from MMC algorithm})}
\label{alg-getmatches}
%\fontsize{10}{10}\selectfont
    \begin{algorithmic}
    \Require $p$ : set of features, $t\in \mathbb{R}$, $features$ : Set of 
    all features
    \State $edges \gets \left\{similarity(f_i, f_j) \mid getImg(f_i)
        \neq getImg(f_j) \wedge f_i, f_j \in p \right\}$
    \If{$\left\vert edges \right\vert > 1$}
        \State $matches \gets MMGet(p, t)$
    \ElsIf{$\left\vert edges \right\vert = 1$}
        \State $matches \gets RatioGet(p, features, t)$
    \Else
        \State $matches \gets \varnothing$
    \EndIf

@@

The matching algorithm for \emph{MMC} detailed in 
Algorithm~\ref{alg-getmatches} finds matches within all partitions with 
more than two elements using the \emph{MM} approach (\emph{MMGet}).  
However, as can be seen in the example in Figure~\ref{fig:graph-view}, 
many of the partitions contain only two feature points from different 
images linked by one edge. In this case, we compare the similarity of 
the these two feature points with their second best match and remove 
matches where this ratio lies above a certain threshold, like in the 
\emph{Ratio} algorithm (\emph{RatioGet}).  For example in the case of 
Figure~\ref{fig:pitts_partition}, we have several feature points from a 
building in one image grouped together with points from the same 
building in another image. If we try to match them globally, the 
differences in similarities are two miniscule to confidently match, 
because setting a threshold this high would lead to wrong matches 
elsewhere, but if we only look at the group of feature points we can use 
\emph{MM} with a much higher threshold and correctly match the points.

@@

@@

\begin{algorithm}[t]
\caption{Ratio Match (\emph{Ratio})}
\label{alg-ratio}
%{\fontsize{10}{10}\selectfont
\begin{algorithmic}
\Require $im_1$ : image, $im_2$ : image, $t \in \mathbb{R}$
\State $matches\gets \varnothing$
\State $features_1 \gets getFeatures(im_1)$
\State $features_2 \gets getFeatures(im_2)$
\ForAll{$f_i \in features_1$}
    \State $f_m,f_n \gets get2NNs(f_i, features_2)$
    \State $ratio \gets d(f_i, f_m) / d(f_i, f_n)$
	\If{$ratio < t$}
        \State $matches \gets \left(f_i, f_m\right)$
	\EndIf
\EndFor
\Return $matches$
\end{algorithmic}
%}
\end{algorithm}

@@

\emph{Spectral} (Algorithm~\ref{alg-spectral}) is based on the spectral 
matching algorithm proposed by Leordeanu and Herbert 
\cite{leordeanu2005spectral}.  The central idea behind it is that the 
set of actual correspondences of feature points between two images 
should be pairwise consistent. That is, given two feature points that 
are geometrically close in one image, for most cases we would assume 
that the closest correspondences of these two points in another image 
would be similarly close.  Based on this assumption we want to pick out 
a set of matches $T \subset S$ where $S$ is the initial set of possible 
matches such that the matches in $T$ are as pairwise consistent as 
possible. If we let $x$ be a binary vector corresponding in length to 
the set of initial matches $S$, where $x_i = 1$ if $m_i \subset T$, then 
we can formulate a subset-score as:
\begin{equation*}
	S = \sum_{m_i, m_j \in T} M(m_i, m_j) = x^TMx
\end{equation*}
The solution $x^{*}$ that maximizes this equation is then $x^{*} = 
argmax(x^TMx)$. By relaxing the constraints on $x$ such that it can take
values in the range of $\left[0, 1\right]$ we can interpret $x_i$ as the
association of $m_i$ with the optimal subset of matches $T$. Because we 
only worry about the relative values of $x$ we can fix the norm of $x$ 
to $1$, in which case by Raleigh's ratio theorem, the $x^{*}$ that 
optimizes $x^TMx$ is the principal eigenvector of $M$.

@@

Since the testing is done on images with partial overlap, the final set 
of matches returned in Algorithm~\ref{alg-spectral} is the set of 
matches where the association of the match with the optimal subset of 
matches, $T$, is above a certain threshold. For the experiments the set 
of initial matches was given by the nearest neighbor of each feature 
point and the threshold was adjusted to allow for the best 50\% to be 
included in the set of final matches. A rate less than 50\% usually did 
not improve results, so to threshold the \emph{Spectral}
algorithm we filter the output using the ratio between first and second
best match as done in \emph{Ratio}.

### 2013-08-13 text/main/ch5_experiments.tex
A few touches on the thesis

In order to demonstrate that the algorithms we propose are in fact 
superior to similar algorithms in the field, we will have to compare 
them. In this chapter we will first describe exactly how we intent to 
test the algorithms and then discuss the results of these comparisons.

\section{Experiments}
For our ideal matching algorithm we would like it to return not only 
correct matches but all possible correct matches when images overlap and 
no matches at all when they don't.  We would like it to work flawlessly 
not just one a few images but on all possible images, and we would 
expect it to run fast even on when faced with tens of thousands of 
feature points.

These requirements fall in to three different categories. We want to 
verify that the algorithm is \emph{accurate}, \emph{general} and 
\emph{fast}.

@@

To convincingly show that the algorithms work for general cases we need 
to demonstrate good recall and precision across a wide range of images.  
However if we are just given to images and a set of matches, there is no
way to tell which matches are correct and which aren't without going 
through them by hand and count them. For any but the simplest cases this
becomes prohibitively time consuming.

A way to circumvent this problem is to restrict the images we test on to 
image pairs that are linked by a homography. Two images linked by a 
homography are tied by a change in perspective such that we given a 
point in one image and the homography we can calculate the corresponding 
position of the point in the other image. Not all image pairs can be 
linked with a homography, something that is intuitive if we image two 
pictures of a playing child. We can't predict the positions of the hands
of the child in the second image with pixel precision just by knowing 
the position of the hands in the first image. However for images where 
all points are situated on a plane or where all the points are far away,
a homography is usually sufficent to describe the pixel transformations 
from one image to the next.

@@

\begin{figure}[htb]
    \makebox[1.0\textwidth][c]{%
        \begin{subfigure}[t]{0.102\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/pair_example1}
			\label{fig:fairey1}
	\end{subfigure}%
		\enspace %add desired spacing between images, e. g. ~, \quad, 
		%(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[t]{0.102\textwidth}
			\centering
			\includegraphics[width=\textwidth]{images/pair_example2}
			\label{fig:fairey2}
		\end{subfigure}%
		\enspace %
        \begin{subfigure}[t]{0.77\textwidth}
   		\centering
   		\includegraphics[width=\columnwidth]{images/crop_examples}
		\end{subfigure}%
	}%
	\caption{Sample test patches produced from an image pair.}
	\label{fig:fairey}
\end{figure}

@@

\begin{figure}[htb]
	\centering
	\includegraphics[width=\columnwidth]{images/graf12345.jpg}
	\caption{Images 1-5 of the Graf set from \cite{mikolajczyk2005performance}.}
	\label{fig:Graf}
\end{figure}

@@

@@

\begin{figure}[htb]
	\begin{subfigure}[c]{0.2\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/graf}
	\end{subfigure}%
	~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[c]{0.8\textwidth}
	\centering
	\includegraphics[width=\columnwidth]{images/result_graf}
	%\caption{Performance on Scharf}
	\end{subfigure}%
	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The 
	plot shows the result of 100 patch pairs generated from the source 
	images shown to the left. The x-axis shows the recall based on the 
accumulated amount of potential matches for all 100 patch pairs. }
	\label{fig:result_graf}
\end{figure}

@@

To further investigate the impact of viewpoint changes, we tested the 
algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
contains 5 images of the same mural taken with gradually increasing 
viewpoint changes.  The first images are almost identical, while the 
last are taken from very different angles. The results from   \emph{MMC} 
and \emph{Ratio} as shown in Figure~\ref{fig:result_viewpoint}, 
confirming that \emph{MMC} is generally superior to \emph{Ratio} across 
viewpoint changes.
The performance of \emph{MM} (not shown in the plot) is similar to 
\emph{MMC}.

@@

In order to investigate whether a geometric algorithm can be improved by
pruning the initial matching set, we tested a hybrid algorithm 
\emph{Spectral-MMC} where matches are selected by \emph{MMC} before 
being filtered by \emph{Spectral}. The results are shown in 
Figure~\ref{fig:result_spectral-mmc} and show that \emph{Spectral-MMC} 
not only outperforms \emph{Spectral} but also improves on \emph{MMC} at 
similar recall rates, illustrating how a geometric algorithm can be 
complemented by a reliable non-geometric pruning of matches.

@@

In terms of computational complexity, \emph{Ratio}, \emph{MM}, and 
\emph{Isomatch} can be implemented in $O(n\log n)$, where $n$ is the 
total number of feature points. The performance of \emph{Spectral} is 
upper bounded by $O(n^{3/2})$. Our current \emph{MMC} implementation has 
a complexity of $O(n^2)$ due to the construction of a similarity matrix 
of the feature points.  However, it is possible to approximate this in 
$O(n\log n)$ using search trees.

@@

\begin{table}[htb]
\caption{Running times as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
3.30~GHz with 8~GB memory.}
\label{table:running_times}
	\centering
%	\small
\begin{tabular}{r*{5}{c}}
\hline
	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} %
& \emph{Isomatch} & \emph{Spectral}	\\
	\noalign{\smallskip} 
	%
	Running time (seconds): & 21 & 23 & 2722 & 1146 & 994\\
	\hline
\end{tabular}
\end{table}

>>>>

In order to demonstrate that the algorithms we propose are in fact 
superior to similar algorithms in the field, we will have to compare 
them with the state of the art. In this chapter we will first describe 
exactly how we intent to compare the algorithms and then discuss the 
results of these comparisons.

\section{Experiments}
For our ideal matching algorithm we would like it to return not just 
some correct matches but all possible correct matches when images 
overlap and no matches at all when they don't.  We would like it to work 
flawlessly not just one a few images but on all possible images, and we 
would expect it to run fast even on when faced with tens of thousands of 
feature points.

These requirements fall in to three different categories. We want to 
verify that the algorithm is \emph{general}, \emph{accurate} and 
\emph{fast}.

@@

To convincingly show that the algorithms work for general cases we need 
to demonstrate good results across a wide range of images.  However if 
we are just given to images and a set of matches, there is no
way to tell which matches are correct and which aren't without going 
through the output by hand and for each match verify that it is correct.  
For any but the simplest cases this becomes prohibitively time 
consuming.

\begin{figure}[tb]
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/homography_possible}
        \caption{Homography possible}
        \label{fig:hom_possible}
    \end{subfigure}%
        \quad %add desired spacing between images, e. g. ~, \quad, (or a 
    %blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/homography_not_possible}
        \caption{Homography not possible}
        \label{fig:hom_impossible}
    \end{subfigure}%
    \caption{Example of images that can and cannot be tied with a 
        homography: Figure~\ref{fig:hom_possible} shows an image pair 
        that can be linked by a homography, since all common areas lie 
        on a plane.  Figure~\ref{fig:hom_impossible} shows an image pair 
        that can't reliably be linked by a homography. Even if we 
        discount the change of people in the scence, the position of the 
        bell compared to the building in the background changes as we 
        change our viewpoint. Images in Figure~\ref{fig:hom_possible} 
        are from the \emph{Murals} dataset while images in 
        Figure~\ref{fig:hom_impossible} are from the Gallagher dataset 
    \cite{gallagher2008}.}
    \label{fig:homography_example}
\end{figure}

A way to circumvent this problem is to restrict the images we test on to 
image pairs that are linked by a homography. Two images linked by a 
homography are are related in a way that means that any point in the 
first image can be translated a point in the second by a linear 
equation. This holds true for two images where the points they have in 
common are situated on a plan, or in the case that the camera only 
rotated in between images. Figure~\ref{fig:homography_example} shows an 
example of an image pair that can be linked with a homography and 
another that cannot. In the second image pair, the change in camera 
position means that pixels can't be linearly translated from one image 
to another. For example would a pixel on the bell be translated to one 
location while an adjacent pixel on the building in the background would
move differently. For this reason we are constrained in which images 
it's possible to test the algorithms on since we cannot evaluate the 
results if the images are not tied by a homography.

@@

\begin{figure}[b]
    \begin{subfigure}[t]{0.102\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/pair_example1}
    \end{subfigure}%
		\enspace %add desired spacing between images, e. g. ~, \quad, 
		%(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[t]{0.102\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/pair_example2}
    \end{subfigure}%
    \enspace %
    \begin{subfigure}[t]{0.77\textwidth}
    \centering
    \includegraphics[width=\columnwidth]{images/crop_examples}
    \end{subfigure}%
    \caption{Sample test patches produced from an image pair.}
	\label{fig:fairey}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[width=\columnwidth]{images/graf12345.jpg}
	\caption{Images 1-5 of the Graf set from \cite{mikolajczyk2005performance}.}
	\label{fig:Graf}
\end{figure}

@@

\begin{figure}[t]
	\begin{subfigure}[c]{0.2\textwidth}
		\centering
		\includegraphics[width=\textwidth]{images/graf}
	\end{subfigure}%
	~ %add desired spacing between images, e. g. ~, \quad, \qquad		  
	%(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[c]{0.8\textwidth}
	\centering
	\includegraphics[width=\columnwidth]{images/result_graf}
	%\caption{Performance on Scharf}
	\end{subfigure}%
	\caption{Accuracy for image pair 1\&3 from the \emph{Graf} set. The 
	plot shows the result of 100 patch pairs generated from the source 
	images shown to the left. The x-axis shows the recall based on the 
accumulated amount of potential matches for all 100 patch pairs. }
	\label{fig:result_graf}
\end{figure}

@@

@@

@@

To further investigate the impact of viewpoint changes, we tested the 
algorithms on the \emph{Graf} image set (Figure~\ref{fig:Graf}), which 
contains 5 images of the same mural taken with gradually increasing 
viewpoint changes.  The first images are almost identical, while the 
last are taken from increasingly different angles. The results from   
\emph{MMC} and \emph{Ratio} as shown in 
Figure~\ref{fig:result_viewpoint}, confirm that \emph{MMC} is generally 
superior to \emph{Ratio} across viewpoint changes. For both methods 
however we see a stark decrease in recall as the viewpoint change 
increases. The performance of \emph{MM} (not shown in the plot) is 
similar to \emph{MMC}.

In order to investigate whether a geometric algorithm can be improved by
pruning the initial matching set, we tested a hybrid algorithm 
\emph{Spectral-MMC} where matches are selected by \emph{MMC} before 
being filtered by \emph{Spectral}. The results are shown in 
Figure~\ref{fig:result_spectral-mmc} and show that \emph{Spectral-MMC} 
not only outperforms \emph{Spectral} but also improves on \emph{MMC} at 
similar recall rates, illustrating how a geometric algorithm can be 
complemented by a reliable non-geometric selection of matches.

@@

\begin{table}[htb]
\caption{Running times as tested on a Intel\textregistered\ Core\texttrademark\ i5-3550 CPU @ 
3.30~GHz with 8~GB memory.}
\label{table:running_times}
	\centering
%	\small
\begin{tabular}{r*{5}{c}}
\hline
	Algorithm: & \emph{Ratio} & \emph{MM} & \emph{MMC} %
& \emph{Isomatch} & \emph{Spectral}	\\
	\noalign{\smallskip} 
	%
	Running time (seconds): & 21 & 23 & 2722 & 1146 & 994\\
	\hline
\end{tabular}
\end{table}
In terms of computational complexity, \emph{Ratio}, \emph{MM}, and 
\emph{Isomatch} can be implemented in $O(n\log n)$, where $n$ is the 
total number of feature points. The performance of \emph{Spectral} is 
upper bounded by $O(n^{3/2})$. Our current \emph{MMC} implementation has 
a complexity of $O(n^2)$ due to the construction of a similarity matrix 
of the feature points.  However, it is possible to approximate this in 
$O(n\log n)$ using search trees.

@@
